|

### 2024-03-06 examples/examples.qmd
updated site output directory

---
#title: "Examples: A Brief Overview"
format:
  html:
    css: styles.css
    theme: cosmo
    #page-layout: full
    #grid:
      #sidebar-width: 250px
      #body-width: 2000px
      #margin-width: 0px
    #gutter-width: 1.5rem

>>>>

---
#title: "Examples: A Brief Overview"
# format:
#   html:
    # css: styles.css
    # theme: cosmo
    #page-layout: full
    #grid:
      #sidebar-width: 250px
      #body-width: 2000px
      #margin-width: 0px
    #gutter-width: 1.5rem

### 2024-03-06 manuscript/manuscript.qmd
updated site output directory

format:
  docx:
    toc: false
  elsevier-pdf:
    journal:
      cite-style: number
      formatting: preprint
      model: 3p
      layout: twocolumn
      #cite-style: number
    include-in-header: 
      text: |
        \newpageafter{author}
  html:
    page-layout: article
    toc: true
    toc-depth: 1
    toc-expand: 2
    toc-title: Table of Contents
    code-tools:
      source: true
      toggle: false
      caption: none
    grid:
      sidebar-width: 350px
      margin-width: 20px

@@

@@

![Types of Stability and Change](./figures/StabilityChange.png){#fig-StablityChange fig-alt="Stability & Change Diagram." width="300" height="300" fig-align="left"}

@@

An ideal longitudinal study integrates (a) a well-articulated theoretical model, (b) an appropriate longitudinal data structure, and (c) a statistical model that is an operationalization of the theoretical model [@collins2006]. To accommodate various research questions and contexts, different types of longitudinal data and data structures have emerged (see Figure **X**). An understanding of these data structures is helpful, as they can warrant different types of longitudinal data analysis (LDA). Given that identifying a starting point for making comparisons is somewhat arbitrary, Curran and Bauer [2019; @bauer2019] provide a nice on-ramp in first distinguishing between the use of “time-to-event” and “repeated measures” data. Although both model time, the former is concerned with whether and when an event occurs, whereas the later is focused on growth and change [@bauer2019]. Time-to-event structures measure time from a well-defined origin point up to the occurrence of an event of interest. This data structure is most often analyzed using survival analysis methods (e.g., hazard rate models, event history analysis, failure-time models) and the time-to-event data can be based on a single assessment or include multiple recurrent or competing events. While much has been written about “time-to-event” data (**see xxx; xxx; xxxx**), including a recent analysis examining exclusionary discipline in schools using data from the ABCD Study (@brislin2023), our emphasis will be given to the modeling of “repeated measures” data.

[![Longitudinal Data Analysis Structural Diagram](./figures/LDAStructure2.png)](https://centerstat.org/resources/)

@@

![Longitudinal Models/Data Structures](./figures/Mindmap1copy.png){#fig-LONGmod fig-alt="Longitudinal Models Diagram." width="300" height="300" fig-align="left"} <br>

@@

![LDA Table](./figures/Tabletemp.png)

>>>>

format:
  docx:
    toc: false
  # elsevier-pdf:
  #   journal:
  #     cite-style: number
  #     formatting: preprint
  #     model: 3p
  #     layout: twocolumn
  #     #cite-style: number
  #   include-in-header: 
  #     text: |
  #       \newpageafter{author}
  ieee-typst: default
  html:
    page-layout: article
    toc: true
    toc-depth: 1
    toc-expand: 2
    toc-title: Table of Contents
    code-tools:
      source: true
      toggle: false
      caption: none
    grid:
      sidebar-width: 350px
      margin-width: 20px

@@

[test](./img/lights.png)
<!-- [Types of Stability and Change](img/StabilityChange.png) -->

@@

<!-- ![Types of Stability and Change](img/StabilityChange.png){#fig-StablityChange fig-alt="Stability & Change Diagram." width="300" height="300" fig-align="left"} -->

@@

An ideal longitudinal study integrates (a) a well-articulated theoretical model, (b) an appropriate longitudinal data structure, and (c) a statistical model that is an operationalization of the theoretical model [@collins2006]. To accommodate various research questions and contexts, different types of longitudinal data and data structures have emerged (see Figure **X**). An understanding of these data structures is helpful, as they can warrant different types of longitudinal data analysis (LDA). Given that identifying a starting point for making comparisons is somewhat arbitrary, Curran and Bauer [2019; @bauer2019] provide a nice on-ramp in first distinguishing between the use of “time-to-event” and “repeated measures” data. Although both model time, the former is concerned with whether and when an event occurs, whereas the later is focused on growth and change [@bauer2019]. Time-to-event structures measure time from a well-defined origin point up to the occurrence of an event of interest. This data structure is most often analyzed using survival analysis methods (e.g., hazard rate models, event history analysis, failure-time models) and the time-to-event data can be based on a single assessment or include multiple recurrent or competing events. While much has been written about “time-to-event” data (**see xxx; xxx; xxxx**), including a recent analysis examining exclusionary discipline in schools using data from the ABCD Study (@brislin2023), our emphasis will be given to the modeling of “repeated measures” data.
manuscript/
<!-- [![Longitudinal Data Analysis Structural Diagram](../img/LDAStructure2.png)](https://centerstat.org/resources/) -->

@@

<!-- ![Longitudinal Models/Data Structures](img/Mindmap1copy.png){#fig-LONGmod fig-alt="Longitudinal Models Diagram." width="300" height="300" fig-align="left"} <br> -->

@@

<!-- ![LDA Table](img/Tabletemp.png) -->
